Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-06-04 _tex/paper2.tex
Built site for gh-pages

\subsection{Further research}\label{sec-discussion_RA}

Four current and new research avenues deserve particular attention due
to their direct impact on the reliability and validity of trait
estimates and the accuracy of statistical inferences. The following
sections outline these avenues and explain how our model provides a
rigorous research framework to investigate them.

>>>>

\subsection{Future research}\label{sec-discussion_RA}

Among the many potential directions for future research, four avenues,
both current and new, deserve particular attention due to their direct
impact on the reliability and validity of trait estimates, as well as on
the accuracy of statistical inferences. The following sections outline
these avenues and explain how our model provides a rigorous research
framework to investigate them.
